\MakeUppercase{Layered Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-06-17 k-planar.tex
Added references for crossing lemma

\begin{lem}
  Every $k$-nearest-neighbour graph is $O(k^2)$ planar.
\end{lem}

@@

>>>>

\begin{lem}\lemlabel{nearest-neighbour}
  Every $k$-nearest-neighbour graph is $O(k^2)$ planar.
\end{lem}

@@

We note that \lemref{nearest-neighbour} is tight up to the leading constant:  Every $n$-vertex nearest neighbour graph has at least $kn/2$ at at most $kn$ edges.  For $k\ge 8$, the Crossing Lemma \cite{ajtai.chvatal.ea:crossing-free,leighton:complexity} implies that the total number of crossings is therefore $\Omega(k^3n)$ so that the average number of crossings per edge is at $\Omega(k^2)$.
